A temporal network analysis of drug co-prescription during antidepressants and anxiolytics dispensing in the Netherlands from 2018 to 2022

### 2025-12-15 docs/submission/GEPI/rebuttal-letter.md

- Section 3.5, paragraph 2 and 3:

  > The distribution of eigenvector centralities exhibited a central peak at intermediate values and heavy tails at both extremes, reflecting the temporal fluctuations of node influence. This pattern arose from the recursive nature of eigenvector centrality, where each node's importance depends on the importance of its neighbors. Aggregating centrality value over time captures the evolving dynamics of the network, where nodes occasionally attain a relatively higher or lower centrality. In contrast, the width of the distribution remained relatively stable, indicating that many co-prescription connections persisted consistently over time.
  > 
  > The eigenvector centrality patterns shown in Figure 2 also highlight the distribution of several subgroups, each distinguished by color. Most subgroup distribution largely overlapped with the general population, represented by the gray density curves. However, two subgroups consistently diverged from this overall pattern: the polypharmacy group and the subset of polypharmacy patiens aged $\geq 65$ years. These subgroups exhibited higher eigenvector centralities across four medication classes, demonstrating a more tightly connected co-prescription patterns within these groups. In addition, the $\geq 65$ years subgroup showed elevated eigenvector centralities in three medication classes, although its magnitude was smaller than that observed in the broader polypharmacy population.

**Comment 2:**  
Abbreviations used in tables and figures (e.g., SD, IQR, ACF, PACF) should be fully spelled out at first use or included in the respective footnotes.

Numerical expressions such as "9.48e-02" are more commonly formatted as "9.48e-2" in standard scientific notation; adopting a consistent style may improve readability.

**Response:**  
All abbreviations have now been fully spelled out at first use in the main text, tables, figures, and the supplementary material to ensure clarity for readers. Moreover, we also revised the supplementary to include the definition of ACF and PACF, also the rationale for using these approaches. All scientific notations have been standardized and formatted as "9.48e-2."

### 2025-12-15 docs/submission/GEPI/manuscript-revision-01/article.tex
Track the revision and its diff

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  number,
  review]{elsarticle}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

\usepackage{fontspec}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{hhline}
\newlength\Oldarrayrulewidth
\newlength\Oldtabcolsep
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{float}
\usepackage{typearea}
\floatplacement{figure}{htbp}
\floatplacement{table}{htbp}
\AtBeginDocument{%
  \storeareas\normalpapersize
}
\BeforeRestoreareas{\cleardoublepage}
\newcommand*\uselandscape{%
  \cleardoublepage
  \KOMAoptions{paper=landscape}%
  \recalctypearea
  \areaset{1.2\textwidth}{1.2\textheight}%
}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\journal{Global Epidemiology}

\usepackage[]{natbib}
\bibliographystyle{elsarticle-num-names}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={A temporal network analysis of drug co-prescription during antidepressants and anxiolytics dispensing in the Netherlands from 2018 to 2022},
  pdfkeywords={Graph Theory, Prescription
Registry, Co-prescription, Mental Health, Public Health Monitoring},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

All data in this study originated from the University of Groningen
IADB.nl, a dynamic pharmacy database containing prescription data since
1994 which still grows expansively. The database covers approximately
128 community pharmacies serving over one million patients and was
accessed on the 20\textsuperscript{th}of September, 2023. All patients
are recorded in the database, irrespective of health care insurance,
where the prescription rates, age, and gender are generalizable to
represent the Netherlands \citep{Visser2013}. The database offers a
longitudinal record, where each individual has a uniquely anonymized
tracking identifier. All records contain fields on the date of
medication dispensing, its quantity, dose regimen, number of days
prescribed, prescribing physicians, and the Anatomical Therapeutic
Chemical (ATC) code. Except for the over the counter drugs and
medication dispensed during hospitalization, all medication records for
each patient are complete, mainly due to high patient-pharmacy
commitment in the Netherlands.

This analysis includes daily drug administration from a static cohort of
adults aged 18 to 65 years and prescribed anxiolytics or antidepressants
at least once in the period 2018-2022.

@@

The choice of centrality largely depends on the objective of network
analysis. As a general guide, degree centrality is useful to identify
popular medication and monitor drug overuse. Betweenness centrality is
suitable for targeting for drug-interaction study and optimizing therapy
plan. Closeness centrality indicates widely-used key medications and
efficiency in treatment networks. Eigenvector centrality is helpful to
identify influential medications and narrow down high-impact medications
for drug monitoring. We defined high and low eigenvector centrality
relative to the expected value \(\frac{1}{n}\), based on the null model
of uniform connectivity (see ``Determining relative importance''). This
study focused on eigenvector centrality to evaluate which medications
have a significant influence on the prescription of antidepressants and
anxiolytics. Equation~\ref{eq-eigen-centrality} outlines the calculation
of eigenvector centrality; \(c_i\) and \(c_j\) are the centralities of
nodes \(\mathcal{v}_i\) and \(\mathcal{v}_j\), respectively, with
\(i, j \in \mathcal{V}\); \(\lambda\) is the eigenvalue;
\(A_{ji}\left(t\right)\) is an element on row \(j\) and column \(i\)
from an adjacency matrix \(A\left(t\right)\), representing the
connection between node \(\mathcal{v}_j\) and \(\mathcal{v}_i\) with
\(i, j \in \mathcal{V}\).

@@

Exploration on seasonality was done on detrended daily, weekly, and
monthly data by generating seasonal plots and calculating the
autocorrelation (ACF) and partial autocorrelation function (PACF).
Seasonal plots were generated for weekly and yearly pattern by using
daily and monthly data, respectively. To generate the seasonal plots,
the data was first deconstructed based on its period. For daily data,
the weekly period was used; while for monthly data, the yearly period
was used. The weekly period was obtained by creating an ordered value
formatted as year - week, e.g.~\texttt{2018\ -\ W01}. Similarly, monthly
period was obtained by creating an ordered value formatted as year -
month, e.g.~\texttt{2018\ -\ M01}. We then grouped the series by its
deconstructed period and visually examine seasonality as overlapping
pattern in most periods. To substantiate the findings, ACF and PACF
plots were used to check on statistical significance of a given pattern.

@@

Classical and seasonal-trend decomposition techniques may not fully
capture complex periodic patterns in time-series data. Singular spectrum
analysis (SSA) is a non-parametric method that leverages Hankel matrix
embedding for decomposition. In this study, SSA was applied to identify
trends and seasonal components in weekly aggregated prescription data.
To better isolate trend and seasonal components, sequential SSA was
applied. First, a basic SSA model with the lag parameter \(L\) = 52 was
used to extract the dominant trend. The residuals were then analyzed
with a second SSA model using \(L = \frac{N}{2}\) to capture complex
periodic patterns. The extracted trend, residuals, and oscillatory
components were evaluated visually and statistically, with Mann-Kendall
trend tests applied to assess long-term changes. A complete
documentation of this approach and its rationale was included in the
supplementary file section S1.1.

@@

Since the sum of all eigenvector centralities \(c_i\) in equation
\ref{eq-eigen-centrality} equals 1, the expected eigenvector centrality
for each node in a uniformly connected network is \(\frac{1}{n}\), where
\(n\) is the total number of nodes. In such a network, each node has an
equal probability of being connected to any other, and thus no node is
more ``influential'' than another. This expected value value,
\(\frac{1}{n}\), serves as a baseline under a null model of uniform
connectivity. Assuming eigenvector centrality scores approximately
follow a normal distribution, we applied a one-sample Student's T-test
with Bonferroni correction to assess how much each eigenvector
centrality differs from the expected values. Nodes with \(c_i\) greater
than \(\frac{1}{n}\) were categorized as having high eigenvector
centrality, and those below the expected value were considered low.

@@

IADB recorded 149,071 patients having at least one dispensing of
antidepressants or anxiolytics within five years of data extraction.
Table~\ref{tbl-overview-patient} captures the demographical dynamics of
the population from 2018 to 2022. The ratio of male to female only
varied slightly, and the average age steadily increased over the year.
These findings imply that the population demography stays relatively
stable overtime without any indication of sudden changes.

@@

\begin{longtable}[c]{|p{0.43in}|p{0.94in}|p{0.94in}|p{0.59in}|p{0.85in}|p{0.85in}}

@@

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{3}{>{\centering}m{\dimexpr 2.47in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Number\ of\ Patients\ (\%)}}}} & \multicolumn{2}{>{\centering}m{\dimexpr 1.7in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Mean\ Age\ (SD)}}}} \\

@@

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Year}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Male}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Female}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Total}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Male}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Female}}}} \\

@@

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2018}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{42,164\ (36.6\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{73,124\ (63.4\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{115,288}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{48.72\ (12.33)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{48.02\ (12.80)}}}} \\

>>>>

% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  number,
  review]{elsarticle}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{5}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage[]{natbib}
\bibliographystyle{elsarticle-num-names}

\usepackage{fontspec}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{hhline}
\newlength\Oldarrayrulewidth
\newlength\Oldtabcolsep
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{float}
\usepackage{typearea}
\floatplacement{figure}{htbp}
\floatplacement{table}{htbp}
\AtBeginDocument{%
  \storeareas\normalpapersize
}
\BeforeRestoreareas{\cleardoublepage}
\newcommand*\uselandscape{%
  \cleardoublepage
  \KOMAoptions{paper=landscape}%
  \recalctypearea
  \areaset{1.2\textwidth}{1.2\textheight}%
}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\journal{Global Epidemiology}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={A temporal network analysis of drug co-prescription during antidepressants and anxiolytics dispensing in the Netherlands from 2018 to 2022},
  pdfauthor={Aly Lamuri; Spyros Balafas; Eelko Hak; Jens H. Bos; Frederike Jörg; Talitha L. Feenstra},
  pdfkeywords={Graph Theory, Prescription
Registry, Co-prescription, Mental Health, Public Health Monitoring},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

All data in this study originated from the University of Groningen
IADB.nl, a dynamic pharmacy database containing prescription records
since 1994. The database covers approximately 128 community pharmacies
serving over one million patients and was accessed on the
20\textsuperscript{th} of September 2023. In the Netherlands, the
primary route of obtaining prescription medications is through community
pharmacies, as physicians issue prescriptions that are almost
exclusively dispensed in these settings. Consequently, the database
provides a comprehensive longitudinal record for each individual,
supported by high patient-pharmacy commitment. All patients are recorded
in the database, irrespective of health care insurance, where the
prescription rates, age, and gender are generalizable to represent the
Netherlands \citep{Visser2013}. Each record includes the dispensing
date, quantity, dose regimen, number of days prescribed, prescribing
physician, and the corresponding Anatomical Therapeutic Chemical (ATC)
code. Medication dispensed during hospitalization and over-the-counter
drugs are not captured, but prescription medication records in community
pharmacies are otherwise complete.

This analysis includes daily drug administration from a static cohort of
adults aged 18 to 65 years and prescribed anxiolytics or antidepressants
at least once in the period 2018-2022. For this study, only a subset of
the database was used to construct the DPN: anonymized patient
identifiers, age, prescription start and end dates, and ATC codes. No
additional individual-level data were included to align with general
data minimization requirements. Other demographic or clinical
information available in the database was not extracted.

@@

The choice of centrality largely depends on the objective of network
analysis. As a general guide, degree centrality is useful to identify
popular medication and monitor drug overuse. Betweenness centrality is
suitable for targeting for drug-interaction study and optimizing therapy
plan. Closeness centrality indicates widely-used key medications and
efficiency in treatment networks. Eigenvector centrality is helpful to
identify influential medications and narrow down high-impact medications
for drug monitoring. We defined high and low eigenvector centrality
relative to the expected value \(C_e = \frac{1}{n}\), based on the null
model of uniform connectivity (see ``Determining relative importance'').
This study focused on eigenvector centrality to evaluate which
medications have a significant influence on the prescription of
antidepressants and anxiolytics. Equation~\ref{eq-eigen-centrality}
outlines the calculation of eigenvector centrality; \(c_i\) and \(c_j\)
are the centralities of nodes \(\mathcal{v}_i\) and \(\mathcal{v}_j\),
respectively, with \(i, j \in \mathcal{V}\); \(\lambda\) is the
eigenvalue; \(A_{ji}\left(t\right)\) is an element on row \(j\) and
column \(i\) from an adjacency matrix \(A\left(t\right)\), representing
the connection between node \(\mathcal{v}_j\) and \(\mathcal{v}_i\) with
\(i, j \in \mathcal{V}\).

@@

Exploration on seasonality was done on detrended daily and weekly data
by generating seasonal plots and calculating the autocorrelation (ACF)
and partial autocorrelation function (PACF). Seasonal plots were
generated for weekly and yearly pattern by using daily and weekly data,
respectively. To generate the seasonal plots, the data was first
deconstructed based on its period. For daily data, the weekly period was
used; while for weekly data, the yearly period was used. The weekly
period was obtained by creating an ordered value formatted as year -
week, e.g.~\texttt{2018\ -\ W01}. Similarly, monthly period was obtained
by creating an ordered value formatted as year - month,
e.g.~\texttt{2018\ -\ M01}. We then grouped the series by its
deconstructed period and visually examine seasonality as overlapping
pattern in most periods. To substantiate the findings, ACF and PACF
plots were used to check on statistical significance of a given pattern.

@@

Classical and seasonal-trend decomposition techniques may not fully
capture complex periodic patterns in time-series data. Singular spectrum
analysis (SSA) is a non-parametric method that leverages Hankel matrix
embedding for decomposition. In this study, SSA was applied to identify
trends and seasonal components in weekly aggregated prescription data.
To better isolate trend and seasonal components, sequential SSA was
applied. First, a basic SSA model with the lag parameter \(L\) = 52 was
used to extract the dominant trend. The residuals were then analyzed
with a second SSA model using \(L = \frac{N}{2}\) to capture complex
periodic patterns. The extracted trend, residuals, and oscillatory
components were evaluated visually and statistically, with Mann-Kendall
trend tests applied to assess long-term changes. A complete
documentation of this approach and its rationale was included in the
supplementary file section S1.2.

@@

Since the sum of all eigenvector centralities \(c_i\) in equation
\ref{eq-eigen-centrality} equals 1, the expected eigenvector centrality
\(C_e\) for each node in a uniformly connected network is
\(\frac{1}{n}\), where \(n\) is 24, representing the total number of
nodes. In such a network, each node has an equal probability of being
connected to any other, and thus no node is more ``influential'' than
another. This expected value, \(\frac{1}{24}\), serves as a baseline
under a null model of uniform connectivity. Assuming eigenvector
centrality scores approximately follow a normal distribution, we applied
a one-sample Student's T-test with Bonferroni correction to assess how
much each eigenvector centrality differs from the expected values. Nodes
with \(c_i\) greater than \(\frac{1}{24}\) were categorized as having
high eigenvector centrality, and those below the expected value were
considered low.

\subsubsection{Subgroup analysis}\label{subgroup-analysis}

Subgroup analyses were conducted by first categorizing the population
into two age groups: \(< 65\) and \(\geq 65\) years \citep{Uddin2022}.
The second categorization was based on general polypharmacy, defined a
receiving \(\geq 5\) medications for at least 30 consecutive days
\citep{nicholson2024prevalence}. These subgroup classifications were
combined to form three comparison pairs: \(< 65\) vs.~\(\geq 65\) years;
non-polypharmacy vs.~polypharmacy; and the non-polypharmacy group aged
\(< 65\) years vs.~the polypharmacy group aged \(\geq 65\) years. A DPN
was generated for each subgroup to calculate its respective eigenvector
centrality.

@@

IADB recorded 149,071 patients with at least one dispensing of
antidepressants or anxiolytics within five years of data extraction.
Table~\ref{tbl-overview-patient} captures the demographical dynamics of
the population from 2018 to 2022. The ratio of male to female only
varied slightly, and the average age steadily increased over the year.
These findings imply that the population demography stays relatively
stable overtime without any indication of sudden changes. Importantly,
the COVID-19 pandemic in 2020 did not substantially influence dispensing
volumes because the community pharmacy remained in service as a part of
nationwide policy. There was no significant disruption in prescription
trends during and after the pandemic, with an average of 2,230,028 in
annual dispensing for all medication classes (standard deviation/SD:
47,478, interquartile range/IQR: 64,009).

@@

\begin{longtable}[c]{|p{0.75in}|p{0.94in}|p{0.94in}|p{0.75in}|p{0.85in}|p{0.85in}}

@@

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{3}{>{\centering}m{\dimexpr 2.63in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Number\ of\ Patients\ (\%)}}}} & \multicolumn{2}{>{\centering}m{\dimexpr 1.7in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Mean\ Age\ (SD)}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{1}}}}} \\

@@

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Year}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Male}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Female}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Total}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Male}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Female}}}} \\

@@

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2018}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{42,164\ (36.6\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{73,124\ (63.4\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{115,288}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{48.72\ (12.33)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{48.02\ (12.80)}}}} \\
